Untitled

### 2023-09-28 code/analysis_Redo.Rmd
Changes in access in far-away zip codes

  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet)
# ,
#          Unemployed = Unemployed / Unemp_denom,
#          Elderly = Age65andOver / TotalPop,
#          Black = Black / TotalPop,
#          Hispanic = Hispanic / TotalPop)

 i <- 10
  df.temp <- df.spill3[,c(1:5, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)) ,
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]

for (i in 11:19){
  df.temp <- df.spill3[,c(1:5, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
}

@@

event_study(data = df.spill3, 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) <= 7) %>% 
  #filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")

@@

df.p %>% 
  filter(Year.y == Att.z) %>% 
  mutate(xcoor = xcoor / Radius, 
         ycoor = ycoor / Radius, 
         popcenter.x = popcenter.x / Radius, 
         popcenter.y = popcenter.y / Radius) %>% 
  filter(Zip == "43604") %>%  #43604
  ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
  #geom_rect(aes(xmin = -SquareSide / 2, xmax = SquareSide / 2, ymin = -SquareSide / 2, ymax = SquareSide / 2), fill = "blue", alpha = 0.2, color = NA) + 
  geom_rect(aes(xmin = -1, xmax = 1, ymin = -1, ymax = 1), fill = "lightgrey", alpha = 0.2, color = NA) + 
  geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) + 
  geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") #+ facet_wrap(~Zip)

>>>>

  left_join(census %>% 
              mutate(Unins.rate = Uninsured / Unins.denom) %>% 
              select(ZipCode, YEAR, TotalPop, IncomeBelowPoverty, PovertyStatusDet, Unins.rate), by = c("Year" = "YEAR", "Zip" = "ZipCode")) %>% 
  left_join(zipsize2 %>% select(GEOID10, ALAND10), by = c("Zip" = "GEOID10")) %>% 
  mutate(Area.SQmiles = ALAND10 / 2.59e6, 
         l.popdensity = log(TotalPop / Area.SQmiles)) %>% 
  mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet) #%>% filter(Zip != '04401')
# ,
#          Unemployed = Unemployed / Unemp_denom,
#          Elderly = Age65andOver / TotalPop,
#          Black = Black / TotalPop,
#          Hispanic = Hispanic / TotalPop)

 i <- 10
  df.temp <- df.spill3[,c(1:5, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)) ,
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]

for (i in 11:19){
  df.temp <- df.spill3[,c(1:5, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
}

@@

event_study(data = df.spill3, 
  yname = "Total.Hours", idname = "Zip", tname = "Year", gname = "Att", estimator = "all") %>% 
  filter(abs(term) <= 7) %>% 
  #filter(estimator %in% c("Gardner (2021)")) %>% 
  ggplot(aes(x = term, y = estimate, color = estimator)) + geom_point(position = position_dodge(0.9)) + geom_errorbar(aes(ymin=estimate-1.96*std.error, ymax=estimate+1.96*std.error), width=.2, position = position_dodge(0.9))  + 
  #facet_wrap(~V1, scales = "free_y", ncol = 3) + 
  theme_tufte_revised() + geom_vline(xintercept=-0.5, color="red", linetype="dashed", alpha=.5) + 
  geom_hline(yintercept=0, color="black", linetype="dashed", alpha=.5) + ggtitle("Total Patients")
```

## Access by quantile
```{r}
qnats1 <- c(0, 0.2, 0.4, 0.6, 0.8)
qnats2 <- c(0.2, 0.4, 0.6, 0.8, 1)

qnats1 <- seq(0, 0.8, by = 0.2)
qnats2 <- seq(0.2, 1, by = 0.2)

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist > quantile(Dist, qnats1[1]) & Dist < quantile(Dist, qnats2[1])), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    TEs <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 2:5){
      model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist < quantile(Dist, qnats2[i])), 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      TEs <- rbind(TEs, data.frame(model.dist.quants$coeftable)[1,])
  }

    TEs

    df.spill3 %>% filter(Zip != '04401')
```

@@

df.p %>% 
  filter(Year.y == Att.z) %>% 
  mutate(xcoor = xcoor / Radius, 
         ycoor = ycoor / Radius, 
         popcenter.x = popcenter.x / Radius, 
         popcenter.y = popcenter.y / Radius) %>% 
 #filter(Zip == "43604") %>%  #43604
  ggplot(aes(x = xcoor, y = ycoor, color = ClinicType)) + 
  #geom_rect(aes(xmin = -SquareSide / 2, xmax = SquareSide / 2, ymin = -SquareSide / 2, ymax = SquareSide / 2), fill = "blue", alpha = 0.2, color = NA) + 
  geom_rect(aes(xmin = -1, xmax = 1, ymin = -1, ymax = 1), fill = "lightgrey", alpha = 0.2, color = NA) + 
  geom_point(position=position_jitter(width=0.05, height=0.05)) + xlim(-2, 2) + ylim(-2, 2) + 
  geom_point(aes(x = popcenter.x, y = popcenter.y), color = "green") + facet_wrap(~Zip)
